---
title: "Triads Pilot I"
author: "Kyle Kurkela"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    df_print: paged
---

```{r setup, include=FALSE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggridges)
library(lme4)

customColSpec <- cols(subject = col_factor())

df <- read_csv('tidy_ret.csv', col_types = customColSpec)

df.enc <- read_csv('tidy_enc.csv', col_types = customColSpec)

df.raw <- read_csv('raw_concatenated.csv')
```

## How well could participants imagine the events?

```{r}
ggplot(df.enc, aes(x = success)) +
  geom_histogram(bins = 30) +
  labs(title = 'Overall Success Ratings Distribution', 
       subtitle = 'How successful were you in imagining a scenario?', 
       caption = '1 - Unsuccessful, 100 = Successful')
```

```{r, warning=FALSE}
psych::describe(df.enc) %>%
  as_tibble(rownames = 'varName') %>%
  filter(varName == 'success') %>%
  select(-vars)
```

```{r}
ggplot(df.enc, aes(x = success, y = subject)) +
  geom_density_ridges(
    jittered_points = TRUE, scale = .95, rel_min_height = .01,
    point_shape = "|", point_size = 3, size = 0.25,
    position = position_points_jitter(height = 0)
  ) +
  labs(title = 'Individual Variability in the Use of the Success Scale', 
       x = 'success (0 = unsuccessful, 100 = successful)', 
       caption = 'dashes = trials')
```

## How long did participants take to respond during encoding?

```{r}
ggplot(df.enc, aes(x = rt, y = subject)) +
  geom_density_ridges(
    jittered_points = TRUE, scale = .95, rel_min_height = .01,
    point_shape = "|", point_size = 3, size = 0.25,
    position = position_points_jitter(height = 0)
  ) +
  labs(title = 'Individual Variability in the use of the success scale', subtitle = 'response times', x = 'rt (ms)', caption = 'dashes = trials') +
  scale_x_continuous(breaks = seq(1000, 40000, 6000))
```

## How well did participants do on the experiment?

```{r, warning=FALSE}
df %>%
  group_by(subject) %>%
  summarise(propCorrect = mean(isCorrect, na.rm = TRUE), .groups = 'drop') -> propCorrectSummarised

ggplot(data = propCorrectSummarised, aes(x = '', y = propCorrect)) +
  geom_point(binaxis = 'y', stackdir = 'center') +
  stat_summary(geom = 'crossbar', fun.data = mean_se, width = 0.2) +
  geom_hline(yintercept = 1/6, color = 'red') +
  expand_limits(y = c(0,1)) +
  labs(title = 'Overall Memory Performance', caption = 'red = chance (1/6 or ~17%), dots = subjects, crossbar = mean +/- se') +
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), aspect.ratio = 1)
```

```{r}
df %>%
  summarise(mean(isCorrect, na.rm = TRUE))
```

Participants performed excellently on the experiment.

## How long did participants take to respond at retrieval?

```{r}
df %>%
  ggplot(aes(x = rt_ret)) +
  geom_histogram(bins = 30) +
  labs(x = 'rt (ms)') +
  scale_x_continuous(breaks = seq(1000,100000,10000))
```

```{r, warning=FALSE}
psych::describe(x = df) %>%
  as_tibble(rownames = 'varName') %>%
  filter(varName == 'rt_ret') %>%
  select(-vars)
```

## How long did participants take to complete the experiment?

```{r}
df.raw %>%
  group_by(subject) %>%
  summarise(time_elapsed_ms = max(time_elapsed), .groups = 'drop') %>%
  mutate(time_elapsed_s = time_elapsed_ms/1000,
         time_elapsed_min = time_elapsed_s/60) %>%
  ggplot(aes(x = '', y = time_elapsed_min)) +
  geom_point() +
  stat_summary(geom = 'crossbar', fun.data = mean_se, width = 0.2) +
  expand_limits(y = c(10,50)) +
  labs(title = 'How Long Participants Took TO Complete the Experiment')
```

## Does successful imagination at encoding predict likelihood of successful memory at retrieval?

```{r}
glmer(isCorrect ~ (1|subject), data = df, family = 'binomial') -> model.fit.0
glmer(isCorrect ~ success + (1|subject), data = df, family = 'binomial') -> model.fit.1
```

```{r}
# likelihood ratio test of the `success` predictor
anova(model.fit.0, model.fit.1)
```

```{r}
df %>%
  filter(!is.na(isCorrect)) -> df.filtered

predict(model.fit.1, type = 'response') -> df.filtered$predictedProbCorrect
predict(model.fit.1, type = 'response', re.form = NA) -> df.filtered$predictedProbCorrectFixed

ggplot(df.filtered, aes(x = success, y = as.numeric(isCorrect))) +
  geom_point(shape = '|', position = position_jitter(width = 0.25, height = 0)) +
  geom_line(aes(group = subject, y = predictedProbCorrect, color = subject), alpha = 0.5) +  
  geom_line(aes(y = predictedProbCorrectFixed), color = 'black', size = 2) +
  geom_hline(yintercept = 1/6, color = 'red', linetype = 'dotted') +
  labs(title = 'Success Ratings At Encoding Predict Retrieval Success',
       y = 'Retrieval Success (Probability)',
       x = 'Self-Reported Imaination Success at Encoding',
       caption = '')
```

```{r}
summary(model.fit.1)
```