---
title: "Data Accounting"
output: 
  html_notebook: 
    toc: yes
    toc_float: yes
---

Packages used  

```{r requirements, warning=FALSE, message=FALSE}
library(tidyverse) # <3
library(rmarkdown)
```

Hand select the data directory. A directory selection window will pop up.  

```{r data_dir}
d <- rstudioapi::selectDirectory()
```

# Data Descriptions

## Rosetta

The rosetta stone data frame (`rosetta`). Hand created by Kyle. Translates the prolific study ids
into English.

```{r rosetta, warning=FALSE, message=FALSE}
file.path('../study_id_rosetta.csv') -> path.2.file

read_csv(file = path.2.file) %>%
  rename(notes = ...4) -> rosetta

paged_table(rosetta)
```

| variable name | description |
| -- | ----------- |
|`study_id`     | the randomized study id provided by prolific. uniquely identifies each prolific study.  |
|`session`      | was this prolific study session 1 or session 2 of the experiment?  |
|`version`      | which version of the experiment was this?  |
|`notes`        | what makes this version unique?  |

## Demographics

The demographics data is downloadable from Prolific. There is one .csv file for each Prolific study. We have 6 studies on Prolific associated with TRIADs: 3 versions, 2 sessions per version. The `study_id` variable is written into the filenames. See code:  

```{r}
# list the full path to all files starting with "prolific_export" in the directory "d"
list.files(path = d, pattern = 'prolific_export.*.csv', full.names = T) -> f.dem

# grab all of the alphanumeric characters between the strings "export_" and ".csv"
str_extract(f.dem, '(?<=export_).*(?=.csv)') -> extracted.study.id

print(f.dem)
```

The `study_id` variable is not written into the data itself. The following code works it into the data appropriately:  

```{r}
# using the read_csv function, read each csv file in "f.dem" in. Store as a list.
df.dem <- map(f.dem, read_csv, show_col_types = F)

# create a tibble with a study_id and dem.data column. dem.data column is a list-col.
tibble(study_id = extracted.study.id, dem.data = df.dem) %>%
  unnest(cols = dem.data) -> df.dem

paged_table(df.dem)
```

| variable name | description |
| ---------- | --------------------------------------------   |
| `study_id` | unique id associated with each Prolific study. |  
| `Submission id` | unique to each subject/study combination. | 
| `Participant id` | unique to each individual. |
| `Status` | did you pay/reject them yet?. |
| `Started at`:`Achived at` | date time that X occurred. |
| `Time taken` | amount of time between originally clicking the link and clicking the link to return. |
| `Completion code` | code that participant can message with. I did not set the option for a completion code. Not sure why it is reported here. |
| `Total approvals`:`Employment status` | demographic data. I did not request any of this information. |

Lets simplify this to a form that is less complex. Using `tidyr::nest` turn all of the demographic data variables into a list column of dataframes.  

```{r}
# take all of the columns that are NOT 'study_id' and 'Participant id' and hide them as a list-col dataframe ("dem.data").  
df.dem %>%
  nest(dem.data = -all_of(c('study_id', 'Participant id'))) -> df.dem

paged_table(df.dem)
```

But what do the study_id's mean to us? Lets add the information from Kyle's `rosetta` dataframe so we understand in English what the `study_id`s mean.  

```{r}
# left_join:
#  - for every row in df.dem, find a matching entry in rosetta. 
#    Add all of the corresponding columns to that row.
#
#  select
#  - rearrange the order of the columns for clarity
left_join(df.dem, rosetta, by = join_by(study_id)) %>%
  select(`Participant id`, study_id, session:notes, dem.data) -> df.dem

paged_table(df.dem)
```

## Experimental

What experimental data do we have?

The experimental data files were designed by the author @KyleK to follow a BIDS format like filenaming convention. See:  

```{r}
# list the full path to all files in directory "d" that end with "data-experiment.csv"
f.exp  <- list.files(path = d, pattern = '.*data-experiment.csv', full.names = T)

print(f.exp[1])
```

| variable | description |  
| - | -- |  
| `datetime` | date and time this file was written |  
| `sub`  | prolific's subject_id |  
| `ses`  |  for V1, prolific's session_id. for V2 + v3, prolific's study_id |  

There are 128 experimental data files:  

```{r}
length(f.exp)
```

What do the data files look like:  

```{r}
# using purr::map and readr::read_csv, read each experimental data .csv file into R as a dataframe
df.exp <- map_dfr(f.exp, read_csv, show_col_types = F)

head(df.exp)
```

A whole lot of variables written by `jsPsych` as programmed by the author @KyleK.  

The important variables for accounting purposes are:

| variable | description |
| - | -- |
| subject_id | first url variable. unique to each subject. |  
| study_id   | second url variable. unique to each Prolific study. |  
| session_id | third url variable. appears to be unique to each subject/study combination. |  

Lets simplify this to a form that is less complex. Using `tidyr::nest` turn all of the experimental data variables into a list column of dataframes.  

```{r}
# Hide some complexity by nesting the data
df.exp %>%
  nest(exp.data = -all_of(c('subject_id', 'study_id'))) -> df.exp

paged_table(df.exp)
```

# Accounting

## Problem 1

### Problem description:

There are 3 subjects who are recorded as "successfully completed" on Prolific who do NOT have an experimental data file associated with their subject id on the server. All 3 of these happened on session 1. 2/3 of these subjects completed session 2 with corresponding data files.  

```{r}
# left_join --
# for every row in df.dem, find a matching entry in df.exp. 
#   If there is not match in df.exp, it will put NULL. for exp.data
left_join(df.dem, df.exp, by = join_by(study_id, `Participant id` == subject_id)) -> dem.exp.df

head(dem.exp.df)
```

```{r}
# Are there entries in dem.exp.df that do NOT have any data files associated with them?
dem.exp.df %>%
  filter(!map_lgl(exp.data, is_tibble)) %>%
  paged_table()
```

```{r}
# the missing subject ids
dem.exp.df %>%
  filter(!map_lgl(exp.data, is_tibble)) %>%
  pull(`Participant id`) -> missing.subjects

dem.exp.df %>%
  filter(`Participant id` %in% missing.subjects)
```

## Problem 2

### Problem Description

There is a data file that has `NA` for both the `subject_id` and the `study_id`.  

```{r}
left_join(df.exp, df.dem, by = join_by(study_id,  subject_id == `Participant id`)) -> exp.dem.df
```

```{r}
exp.dem.df %>%
  filter(!map_lgl(dem.data, is_tibble))
```

## The Numbers

How many subject completed each session according to the demographics and experimental data?

```{r}
df.dem %>%
  count(version, session)
```

```{r, warning=FALSE, message=FALSE}
df.exp %>%
  left_join(rosetta) %>%
  count(version, session)
```

Alternative View

```{r}
df.dem %>%
  count(`Participant id`, session) %>%
  complete(`Participant id`, session, fill = list(n = 0)) %>%
  pivot_wider(names_from = session, values_from = n) %>%
  mutate(type = case_when(session1 == 1 & session2 == 1 ~ 'did both',
                          session1 == 1 & session2 == 0 ~ 'did not return for session 2',
                          TRUE ~ NA)) %>%
  count(type)
```
```{r, warning=FALSE, message=FALSE}
df.exp %>%
  left_join(rosetta) %>%
  count(subject_id, session) %>%
  complete(subject_id, session, fill = list(n = 0)) %>%
  pivot_wider(names_from = session, values_from = n) %>%
  mutate(type = case_when(session1 == 1 & session2 == 1 ~ 'did both',
                        session1 == 1 & session2 == 0 ~ 'did not return for session 2',
                        session1 == 0 & session2 == 1 ~ 'has session 2 but no session 1?',
                        TRUE ~ NA)) %>%
  count(type)
```

