---
title: "Check Subject Exclusions"
author: "Kyle Kurkela"
date: "2023-05-11"
output: 
  html_document: 
    toc: yes
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rmarkdown)
library(ggridges)

tidy.enc <- read_rds('../tidy_enc.rds')
tidy.ret <- read_rds('../tidy_ret.rds')
tidy.bds <- read_rds('../tidy_bds.rds')
tidy.catch <- read_rds('../tidy_catch.rds')
```

## Exclusion Criterion 1

Participants who are statistical outliers (3 standard deviations below the mean)
for reaction time for any 1 of our tasks.

### Encoding RTs

```{r}
# encoding
tidy.enc %>%
  group_by(subject_id, study_id) %>%
  summarise(mean_rt_slider = mean(rt_slider), .groups = 'drop') %>%
  group_by(study_id) %>%
  mutate(zscore = as.double(scale(mean_rt_slider))) %>%
  ungroup() %>%
  mutate(exclude_enc = zscore < -3) %>%
  mutate(mean_rt_slider = mean_rt_slider / 1000) %>%
  paged_table()
```

```{r}
tidy.enc %>%
  mutate(rt_slider = rt_slider / 1000) %>%
  ggplot(aes(x = rt_slider, y = subject_id, height = stat(density))) +
  geom_density_ridges(
    jittered_points = TRUE,
    position = position_points_jitter(width = 0.05, height = 0),
    point_shape = '|', point_size = 3, point_alpha = 1, alpha = 0.7,
  ) +
  scale_x_continuous(breaks = c(0, 10000, 20000, 48500, 146000)/1000) +
  labs(x = 'slider_rt (s)', title = 'Encoding Slider Response', subtitle = 'RT Distributions')
```


### Cued Recall RTs

```{r}
# cued recall
tidy.ret %>%
  group_by(subject_id, study_id) %>%
  summarise(mean_rt_cued_recall = mean(rt), .groups = 'drop') %>%
  group_by(study_id) %>%
  mutate(zscore = as.double(scale(mean_rt_cued_recall))) %>%
  ungroup() %>%
  mutate(exclude_ret = zscore < -3) %>%
  paged_table()
```

```{r}
tidy.ret %>%
  mutate(rt = rt / 1000) %>%
  ggplot(aes(x = rt, y = subject_id, height = stat(density))) +
  geom_density_ridges(
    jittered_points = TRUE,
    position = position_points_jitter(width = 0.05, height = 0),
    point_shape = '|', point_size = 3, point_alpha = 1, alpha = 0.7,
  ) +
  scale_x_continuous(breaks = c(0,30, 60, 90, 120, 540)) +
  labs(x = 'slider_rt (s)', title = 'Cued Recall', subtitle = 'Submit RT Distributions')
```


### BDS RTs

```{r}
# bds
tidy.bds %>%
  group_by(subject_id, study_id) %>%
  summarise(mean_rt_bds = mean(rt), .groups = 'drop') %>%
  group_by(study_id) %>%
  mutate(zscore = as.double(scale(mean_rt_bds))) %>%
  ungroup() %>%
  mutate(exclude_bds = zscore < -3) %>%
  paged_table()
```

```{r}
tidy.bds %>%
  mutate(rt = rt / 1000) %>%
  ggplot(aes(x = rt, y = subject_id, height = stat(density))) +
  geom_density_ridges(
    jittered_points = TRUE,
    position = position_points_jitter(width = 0.05, height = 0),
    point_shape = '|', point_size = 3, point_alpha = 1, alpha = 0.7,
  ) +
  scale_x_continuous(breaks = c(0,5, 10, 15, 20, 25)) +
  labs(x = 'slider_rt (s)', title = 'Backwards Digit Span', subtitle = 'RT Distributions')
```


## Exclusion Criterion 2

Participants who objectively demonstrated clear low-effort throughout the experiment. Specifically participants are missing responses from more than 90% of cued recall trials.

```{r}
tidy.ret %>%
  pivot_longer(cols = starts_with('ret_resp'), names_to = 'resp_num', values_to = 'text_resp') %>%
  group_by(subject_id) %>%
  summarise(nblank = sum(text_resp == ""), total = n(), .groups = 'drop') %>%
  mutate(prop_blank = nblank / total) %>%
  mutate(exclude = prop_blank > .9) %>%
  paged_table()
```

## Exclusion Criterion 3

Participants who objectively demonstrated clear low-effort throughout the experiment. Specifically participants used the same response on the slider scale for every single encoding trial.

```{r}
tidy.enc %>%
  group_by(subject_id, study_id) %>%
  summarise(sd_slider = sd(response_slider), .groups = 'drop') %>%
  mutate(exclude = sd_slider == 0) %>%
  paged_table()
```

## Exclusion Criterion 4

Participants who objectively demonstrated clear low-effort throughout the experiment. Specifically participants used the same response on the slider scale for every single encoding trial.

```{r}
# catch trials
tidy.catch %>%
  select(subject_id, study_id, response) %>%
  paged_table()
```

## Exclusion Criterion 5

Participants who did not comprehend the instructions. Failed 2 of 3 instructions comprehension tests.
