---
title: "Timespent Analysis"
author: "Kyle Kurkela"
date: "2023-05-12"
output: 
  html_document: 
    toc: yes
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

df <- read_rds('../compiled_experiment.rds')
```

See code chunk below for Kyle's tidying process

```{r tidy}
df %>%
  filter(phase %in% c('enc', 'bds', 'ret')) %>%
  arrange(subject_id, study_id, trial_index) %>%
  group_by(subject_id, study_id, phase) %>%
  slice(c(1,n())) %>%
  group_by(subject_id, study_id, phase) %>%
  summarise(time_spend = diff(time_elapsed), trial_index = max(trial_index), .groups = 'drop') -> timespent.task

df %>%
  filter(!phase %in% c('bds', 'enc', 'ret')) %>%
  arrange(subject_id, study_id, trial_index) %>%
  select(subject_id, study_id, trial_index, phase, rt) %>%
  filter(!is.na(rt)) %>%
  mutate(rt = as.double(rt)) %>%
  rename(time_spend = rt) -> timespent.all.else

timespent.all.else %>%
  bind_rows(., timespent.task) %>%
  arrange(subject_id, trial_index) %>%
  mutate(time_spend = time_spend / 1000 / 60) -> tidy.timespend

set.seed(321)
SelectColors <- sample(grDevices::rainbow(n = 14), 14)
```

## How much time did participants send in each phase of the experiment?

```{r}
tidy.timespend %>%
  arrange(study_id, subject_id, trial_index) %>%
  rmarkdown::paged_table()
```

A Pageable Table to explore. Where:

- `subject_id` = arbitrary label given by Kyle  
- `trial_index` = arbitrary numeric label given to each phase, designed to sort them in chronological order
- `phase` = arbitrary labels given to the different parts of the experiment. Should be easy enought to figure out.
- `time_spend` = estimated amount of time (in minutes) spend on each phase  
- `study_id` = session 1 or session 2

## Which phases were participants most variable?

```{r}
tidy.timespend %>% 
  group_by(study_id, phase) %>% 
  summarize(across(time_spend, sd), .groups = 'drop') %>%
  rename(time_spend_sd = time_spend) %>%
  arrange(study_id, desc(time_spend_sd)) %>%
  rmarkdown::paged_table()
```

Session two is at the end of the table. Click through to see.

## Can we make a pretty visual?

```{r}
ggplot(tidy.timespend, aes(x = subject_id, y = time_spend)) +
  geom_col(aes(fill = phase), color = 'black') +
  geom_label(stat = 'summary', fun = sum, aes(label = round(after_stat(y), 1))) +
  scale_fill_manual(values = SelectColors) +
  labs(y = 'time spent (min)', 
       x = 'subject', 
       title = 'Where did subject spend their time?', 
       caption = 'Colors sorted in chronological order from bottom to top. Labels are total time spent on session (min).') +
  facet_grid(~study_id)
```

I tried my best with the colors ::grimace::.

### Zoom in on ret

```{r}
tidy.timespend %>%
  filter(phase == 'ret') %>%
  ggplot(aes(x = subject_id, y = time_spend, fill = phase)) +
  geom_col() +
  geom_label(aes(label = round(time_spend, 1), fill = NULL)) +
  scale_fill_manual(values = SelectColors[5]) +
  labs(y = 'time spent (min)', x = 'subject', title = 'Subject 5 spent ~30 minutes on the cued recall alone') +
  scale_y_continuous(limits = c(0, 60)) +
  facet_grid(~study_id)
```

See the reaction time distributions for `s005`. They had a single cued recall trial where they had a reaction time of almost 9 minutes!!

### Zoom in on instr_pre_bds

```{r}
tidy.timespend %>%
  filter(phase == 'instr_pre_bds') %>%
  ggplot(aes(x = subject_id, y = time_spend, fill = phase)) +
  geom_col() +
  geom_label(aes(label = round(time_spend, 1), fill = NULL)) +
  scale_fill_manual(values = SelectColors[8]) +
  labs(y = 'time spent (min)', x = 'subject', title = 'Subject 1 spent ~17 minutes on the backwards digit span instructions...') +
  scale_y_continuous(limits = c(0, 60)) +
  facet_grid(~study_id)
```

Maybe `s004` was taking a break?

### Zoom in on encoding

```{r}
tidy.timespend %>%
  filter(phase == 'enc') %>%
  ggplot(aes(x = subject_id, y = time_spend, fill = phase)) +
  geom_col() +
  geom_label(aes(label = round(time_spend, 1), fill = NULL)) +
  scale_fill_manual(values = SelectColors[length(SelectColors)-5]) +
  labs(y = 'time spent (min)', x = 'subject', title = 'Significant Variability in Encoding Time to Completion') +
  scale_y_continuous(limits = c(0, 60)) +
  facet_grid(~study_id)
```

Nothing seems too crazy here. The range is pretty substantial though 9 - 17 minutes.  

### Zoom in Welcome Screen

```{r}
tidy.timespend %>%
  filter(phase == 'welcome_screen') %>%
  ggplot(aes(x = subject_id, y = time_spend, fill = phase)) +
  geom_col() +
  geom_label(aes(label = round(time_spend, 1), fill = NULL)) +
  scale_fill_manual(values = SelectColors[length(SelectColors)]) +
  labs(y = 'time spent (min)', x = 'subject', title = 'Subject spent significant time one welcome screen') +
  scale_y_continuous(limits = c(0, 60)) +
  facet_grid(~study_id)
```

Participants will sometimes click into the experiment but then sit on the welcome screen.  

## How long do participants spent completing the survey?

```{r}
tidy.timespend %>%
  filter(phase %in% c('sam', 'iri', 'vviq')) %>%
  ggplot(aes(x = subject_id, y = time_spend, fill = phase)) +
  geom_col(color = 'black') +
  scale_y_continuous(breaks = c(0,3,6,9,12)) +
  scale_fill_manual(values = SelectColors[1:3]) +
  expand_limits(y = c(0,12)) +
  labs(title = 'How log did participants spend on the surveys?')
```

