---
title: "Secondary Exclusion Criteria"
author: "Kyle Kurkela"
date: "2023-05-12"
output:
  html_document: 
    toc: yes
    code_folding: hide  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

df.interaction <- read_rds('../compiled_interaction.rds')
df.experiment <- read_rds('../compiled_experiment.rds')
df.graded <- read_rds('../graded_df.rds')

df.sam <- read_rds('../tidy_sam.rds')
df.iri <- read_rds('../tidy_iri.rds')
df.vviq <- read_rds('../tidy_vviq.rds')
```

## Criterion 1: RT Slower than 5 minutes

Reaction time on any 1 trial is slower than 5 minutes.

```{r, warning=FALSE}
# coerce rt to double
# remove events without a rt
df.experiment %>% 
  filter(!is.na(rt)) %>%
  group_by(subject_id, study_id) %>%
  summarise(exclude = any(rt > 5*60*1000), .groups = 'drop') %>%
  pivot_wider(names_from = study_id, values_from = exclude) %>% 
  rmarkdown::paged_table()
```

```{r}
df.experiment %>%
  filter(!is.na(rt)) %>%
  mutate(highlight = rt > 5*60*1000) %>%
  mutate(rt = rt/1000/60) %>%
  ggplot(aes(x = rt, y = phase)) +
  geom_point(shape = "|", size = 3) +
  facet_grid(study_id~subject_id) +
  geom_vline(xintercept = 5, color = 'red') +
  scale_color_manual(values = c('black', 'red')) +
  theme_light() +
  guides(color = "none") +
  theme(panel.grid.minor.x = element_blank()) +
  scale_x_continuous(breaks = c(0,1,5,10,15)) +
  labs(x = 'rt (min)', caption = 'dashes = trials. red line is 5 minutes')
```

## Criterion 2: Cued Recall Performance > 3 SDs

Cued recall performance in greater than 3 SDs away from sample mean

```{r}
df.graded %>%
  select(subject_id, study_id, trial_index, encTrialNum, ends_with('Correct')) %>%
  pivot_longer(cols = ends_with('Correct'), names_to = 'position', values_to = 'correct') %>%
  filter(!is.na(correct)) %>%
  group_by(subject_id, study_id) %>%
  summarise(prop_correct = mean(correct), .groups = 'drop') %>%
  # z score within session (study_id)
  group_by(study_id) %>%
  mutate(zscore = as.double(scale(prop_correct))) %>%
  mutate(exclude = abs(zscore) > 3) %>%
  arrange(study_id, subject_id) %>%
  rmarkdown::paged_table()
```

Zscore within session. See code.

## Criterion 3: RT on Surveys < 3 SDs

Average RT to complete the debriefing, SAM, IRI, or VVIQ is faster than 3 SDs away from sample mean.

```{r}
bind_rows(df.sam, df.iri, df.vviq, .id = 'survey') %>%
  mutate(survey = factor(survey, labels = c('sam', 'iri', 'vviq'))) %>%
  select(subject_id, rt, survey) %>%
  # zscore within survey
  group_by(survey) %>%
  mutate(zscore = as.double(scale(rt))) %>%
  mutate(exclude = abs(zscore) > 3) %>%
  rmarkdown::paged_table()
```

## Criterion 4: > 5 blue or focus events

If they have more than 5 blur or focus events during the course of the experiment.

```{r}
# give the subjects easier to read ids
# count the number of browser events
# create an easy to read table
df.interaction %>%
  unnest(data) %>%
  count(subject_id, session_id, event) %>%
  complete(nesting(subject_id, session_id), event, fill = list(n = 0)) %>%
  filter(event %in% c('blur', 'focus')) %>%
  pivot_wider(names_from = event, values_from = n) %>%
  mutate(exclude = blur > 5 | focus > 5) %>%
  rmarkdown::paged_table()
```

Due to a bug in my code, I wrote out the "session_id" instead of the "study_id" which correctly identifies the study session. I am not entirely sure what Prolific's "session_id" refers to.
