---
title: "Depdendency Results Change as a Result of Winsorizing"
date: "`r Sys.Date()`"
author: "Kyle Kurkela"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    df_print: paged
params:
  winsorLow: 0.05
  winsorHigh: 0.95
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lmerTest)
library(report)

graded.df <- read_rds('tidy_data/graded_df.rds')
dependency.df <- read_rds('tidy_data/tidy_dependency.rds')
```

# Winsorize Data

A table of total recall performance for each subject x session x condition.

```{r}
(graded.df %>%
  dplyr::select(subject_id, study_id, session_id,
                session, condition, encTrialNum,
                trial_index, ends_with('Correct')) %>%
  pivot_longer(cols = ends_with('Correct'), names_to = 'position', values_to = 'correct') %>%
  filter(!is.na(correct)) %>%
  group_by(subject_id, session, condition) %>%
  summarise(across(correct, mean), .groups = 'drop') %>%
  mutate(numCorrect = correct * 72, total = 72) %>%
  arrange(correct, subject_id, session, condition) -> performance.df)
```

Remove subjects if they have extreme performance in any one condition:

```{r}
# filter out subjects IF they have any extreme condition
performance.df %>%
  filter(correct > params$winsorLow & correct < params$winsorHigh) %>%
  count(subject_id) %>%
  filter(n == 4) %>%
  pull(subject_id) -> goodSs

dependency.df %>%
  filter(subject_id %in% goodSs) -> dependency.df
```

### Is there dependency?

```{r}
dependency.df %>% 
  group_by(subject_id) %>% 
  summarise(across(starts_with('joinedRetrieval'), mean), .groups = 'drop') -> tmp.df

joinedRetrieval.data <- tmp.df$joinedRetrieval.data
joinedRetrieval.indep <- tmp.df$joinedRetrieval.indep

# paired t-test
t.test(joinedRetrieval.data, joinedRetrieval.indep, paired = T) -> testResult

# nice summary using report
report(testResult) %>% 
  summary()
```

### Dependency as a function of session/condition?

```{r}
ggplot(dependency.df, aes(x = condition, y = dependency)) +
  geom_point(alpha = 0.4) +
  geom_line(aes(group = subject_id), alpha = 0.4) +
  stat_summary(geom = 'crossbar', fun.data = mean_se, width = 0.2, fill = 'white') +
  scale_y_continuous(limits = c(NA, 0.5)) +
  theme_classic() +
  labs(title = 'Dependency', 
       subtitle = str_glue('On Winsorized Subsample (n = {n})', n = length(goodSs)), 
       y = 'Dependency', x = 'Triad Type') +
  guides(color = "none") +
  facet_wrap(~session, ncol = 2) -> plotB

ggsave(filename = 'figures/Figure2_winsor_595.png', 
       plot = plotB, 
       width = 7, height = 5, dpi = 600,
       device = 'png', units = 'in')

plotB
```

Fit a linear mixed effects model:

```{r}
lmer(dependency ~ session * condition + (1|subject_id), data = dependency.df) -> model1.fit

summary(model1.fit)
```

Get a nice report from `report`:

```{r}
report(model1.fit) -> rep1

summary(rep1)
```

### partial correlation tests?

```{r}
dependency.df %>%
  unite(col = 'sess_cond', session, condition) %>%
  pivot_wider(id_cols = subject_id, names_from = sess_cond, values_from = dependency) %>%
  dplyr::select(-subject_id) %>% as.list() -> x
```

Famous Person ~~ Famous Person

```{r}
(ppcor::pcor.test(x = x$`session1_famous person`,
                 y = x$`session2_famous person`,
                 z = c(x$`session1_famous place`, x$`session2_famous place`)) -> result1)
```

Famous Place ~~ Famous Place

```{r}
(ppcor::pcor.test(x = x$`session1_famous place`,
                  y = x$`session2_famous place`,
                  z = c(x$`session1_famous person`, x$`session2_famous person`)) -> result2)
```

### figure y

```{r}
# pivot wider. calculate bias
dependency.df %>%
  pivot_wider(id_cols = all_of(c('subject_id', 'session')), 
              names_from = condition, values_from = dependency) %>%
  group_by(subject_id) %>%
  mutate(person_prefer = `famous person` > `famous place`,
         place_prefer = `famous person` < `famous place`) %>%
  mutate(type = case_when(sum(person_prefer) == 2 ~ 'strong person bias',
                          sum(place_prefer) == 2 ~ 'strong place bias',
                          TRUE ~ 'ambiguous')) %>%
   mutate(bias = `famous person` - `famous place`) -> figureData
```

```{r}
ggplot(figureData, aes(x = session, y = bias, color = type)) +
  geom_point() +
  geom_line(aes(group = subject_id)) +
  facet_grid(~type) +
  scale_color_manual(values = c('black', 'blue', 'red')) +
  guides(color = 'none') +
  labs(title = str_glue('Winsorized Data (n = {n})', n = length(goodSs)))
```

### figure z

```{r}
# summarise over session. pivot wider.
dependency.df %>%
  group_by(subject_id, condition) %>%
  summarise(across(.cols = dependency, .fns = mean), .groups = 'drop') %>%
  pivot_wider(names_from = 'condition', values_from = 'dependency') -> summarised.df
```


```{r}
ggplot(figureData, aes(x = `famous person`, y = `famous place`)) +
    guides(color = 'none') +
    theme_minimal() +
    scale_x_continuous(limits = c(-0.025, .45)) +
    scale_y_continuous(limits = c(-0.025, .45)) +
    theme(aspect.ratio = 1) +
    geom_abline(slope = 1, intercept = 0, linetype = 'solid') +
    annotate(geom = 'polygon', x = c(0,0,.45), y = c(0,.45,.45), alpha = 0.3, fill = scales::muted('red')) +
    annotate(geom = 'label', x = 0.1, y = 0.4, label = '"place" bias', color = scales::muted('red')) +
    annotate(geom = 'polygon', x = c(0,.45,.45), y = c(0,0,.45), alpha = 0.3, fill = scales::muted('blue')) +
    annotate(geom = 'label', x = 0.4, y = 0.1, label = '"person" bias', color = scales::muted('blue')) +
    geom_point(data = summarised.df, shape = 'asterisk', size = 2) +
  labs(title = str_glue('Winsorized Data (n = {n}', n = length(goodSs)))
```

### Still the U shape relationship?

```{r}
dependency.df %>%
  group_by(subject_id) %>%
  summarise(dependency = mean(dependency)) -> dependency.summarised

graded.df %>%
  pivot_longer(cols = ends_with('Correct'), names_to = 'type', values_to = 'isCorrect') %>%
  filter(!is.na(isCorrect)) %>%
  group_by(subject_id) %>%
  summarise(retrieval_success = mean(isCorrect), .groups = 'drop') -> graded.summarized

dependency.summarised %>%
  left_join(., graded.summarized, by = join_by('subject_id')) -> df
```

```{r}
ggplot(df, aes(x = retrieval_success, y = dependency)) +
  geom_point() +
  geom_smooth(method = 'lm', formula = y ~ x + I(x^2)) +
  labs(title = str_glue('{params$winsorLow*100}%/{params$winsorHigh*100}% Subsample (n = {n})', 
                        n = length(goodSs)),
       x = 'Overall Accuracy',
       y = 'Dependency') +
  scale_x_continuous(limits = c(0,1), breaks = c(0, 0.25, 0.5, .75, 1)) +
  theme_classic() -> plotA

write_rds(plotA, file = str_glue('figures/winsor-{params$winsorLow*100}{params$winsorHigh*100}_plt.Rds'))

plotA
```

```{r}
lm(dependency ~ retrieval_success + I(retrieval_success^2), data = df) -> model.fit

summary(model.fit)
```
```{r}
report(model.fit) -> rep1

summary(rep1)
```

