---
title: "Kurkela Dependency vs Horner Dependency"
author: "Kyle Kurkela"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
    code_folding: hide
    df_print: paged
---

```{r setup, include = FALSE}
library(tidyverse)
```


How do my dependency calculations compare with those from [Aiden Horner (Bisby et al. 2018)](https://figshare.com/articles/software/Model_code/5240752)?  
  
## Kyle's Calculations:  

See `09_calculate_dependency.R`.  
  
The Results look like this:  

```{r}
tidy.dependency <- read_rds('tidy_data/tidy_dependency.rds')

head(tidy.dependency)
```

For every subject (62), session (2), condition (2) combination (total = 248), three different numbers are calculated:

| calculation | description |
| ---------   | ----------- |
| `joinedRetreival.data`  | the average proportion of joined retrieval averaged across 6 contingency tables as observed in the data. | 
| `joinedRetreival.indep` | the average proportion of joined retrieval averaged across 6 contingency tables as estimated assuming independence. |
| `dependency` | `joinedRetreival.data` - `joinedRetrieval.indep` |

## Horner Calculations:

[Aiden Horner's Dependency MATLAB script as released with Bisby et al. 2018](https://figshare.com/articles/software/Model_code/5240752):

```{MATLAB, eval = FALSE}
function [dep] = Dependency(res,pair,guess,c)
%% Function to calculate behavioural dependency measure
%  Aidan J Horner 04/2015

% input:
% res       =   MxN matrix of M 'events' and N 'retrieval trials'
% pair      =   pair of retrieval trials to calculate dependency 
%               (e.g., cue location retrieve object and cue location retrieve person)
%               example = [1 2] - uses first two columns to build contingency table for analysis
% optional inputs:
% guess     =   include guessing in Dependent Model (1 or 0)
%               default = 1
% c         =   number of choices (i.e., c-alternative forced choice) - for
%               estimating level of guessing
%               default = 6

% output:
% dep       =   dependency measure for [data independent_model dependent_model]

%% housekeeping

if nargin   < 3
    guess   = 1;                                            % set 'guess' to 1 if not defined by user
    c       = 6;                                            % set 'c' to 6 if not defined by user
end

%% calculate dependency for data
 
res2        = res(:,pair);                                  % create column Mx2 matrix for retrieval trials defined by 'pair'
dep(1)      = sum(sum(res2,2)~=1)/size(res2,1);         	% calculate dependency for data

%% calculate dependency for independent model

acc         = mean(res2,1);                                 % calculate accuracy for each retrieval type
dep(2)      = ((acc(1)*acc(2))+((1-acc(1))*(1-acc(2))));    % calculate dependency for independent model

%% calculate dependency for dependent model

cont        = nan(size(res2,1),2,2);                        % create matrix for dependent model probabilities
g           = (1-mean(res(:)))*(c/(c-1));                   % calculate level of guessing
b           = mean(res); b(:,pair) = nan;                   % calculate average performance
for i       = 1:size(res2,1)                                % loop through all event   
    a       = res(i,:); a(:,pair) = nan;                    % calculate event specific performance
    E       = mean(a,'all','omitmissing')/mean(b,'all','omitmissing');                        % calculate ratio of event / average performance (episodic factor)
    for p = 1:2;
        if E*acc(p)>1
            P(p) = 1;
        else
            if guess == 1
                P(p) = (E*(acc(p)-(g/c)))+(g/c);
            elseif guess == 0
                P(p) = E*acc(p);
            end
        end
    end
    cont(i,1,1) = P(1)*P(2);
    cont(i,1,2) = (1-P(1))*P(2);
    cont(i,2,1) = P(1)*(1-P(2));
    cont(i,2,2) = (1-P(1))*(1-P(2));
end
cont2       = squeeze(sum(cont));                           % create contingency table
dep(3)      = (cont2(1,1)+cont2(2,2))/sum(cont2(:));        % calculate dependency for dependent model
```

  
See my application of Aiden's script to our data in `09_calculate_dependency_horner.R`.  
  
The results looks like this:  

```{r}
tidy.horner <- read_rds('tidy_data/tidy_horner.rds')

head(tidy.horner)
```

For every subject (62), session (2), condition (2) combination (total = 248), the following are calculated:

| calculation | description |
| ---------   | ----------- |
| `Data_Ab_Ac`:`Data_Ca_Bc` | To match Horner and colleagues descriptions, I relabeled our experimental variables to match theirs. A = `key`, B = `objOne`, C = `objTwo.` These variables represent estimated joined retrieval observed in the data for each of these 6 contingency tables. | 
| `Indep_Ab_Ac`:`Indep_Ca_Bc` | To match Horner and colleagues descriptions, I relabeled our experimental variables to match theirs. A = `key`, B = `objOne`, C = `objTwo.` These variables represent estimated joined retrieval under the independent model for each of the 6 contingency tables. | 
| `Depend_Ab_Ac`:`Depend_Ca_Bc` | To match Horner and colleagues descriptions, I relabeled our experimental variables to match theirs. A = `key`, B = `objOne`, C = `objTwo.` These variables represent estimated joined retrieval under the dependent model for each of the 6 contingency tables. |
| `Data` | Average of `Data_AbAc`:`Data_CaBc`. | 
| `Indep` | Average of `Indep_AbAc`:`Indep_CaBc`. | 
| `Depend` | Average of `Depend_AbAc`:`Depend_CaBc`. | 

## How do our calculations compare?

```{r}
# tidy up the condition column to match the horner table
tidy.dependency %>%
  mutate(condition = str_remove(condition, ' ')) -> tidy.dependency

# join the two tables together, matching the rows
left_join(tidy.dependency, tidy.horner, 
          by = join_by('subject_id' == 'subj', 'session' == 'sess', 'condition' == 'cond')) -> joined.df
```

```{r}
joined.df %>%
  dplyr::select(joinedRetrieval.data, joinedRetrieval.indep, dependency, Data, Indep, Depend) %>%
  corrr::correlate(quiet = T) %>%
  corrr::shave(upper = F) %>%
  corrr::stretch(na.rm = T) -> figure.df

axis.sort <- c('joinedRetrieval.data', 'joinedRetrieval.indep', 'dependency', 'Data', 'Indep', 'Depend')

ggplot(figure.df, aes(x = x, y = y, fill = r, label = round(r, 2))) +
  geom_tile() +
  geom_text() +
  scale_x_discrete(limits = axis.sort) +
  scale_y_discrete(limits = rev(axis.sort)) +
  theme_minimal() +
  theme(axis.title = element_blank(), axis.text.x = element_text(angle = 90), panel.grid = element_blank()) +
  scale_fill_gradient2() +
  labs(title = "Kurkela's calculations vs Horner's calculations")
```


### Kyle's Independence vs Horner's Independence

```{r}
ggplot(joined.df, aes(x = Indep, y = joinedRetrieval.indep)) +
       geom_point() +
       geom_smooth(method = 'lm', formula = y ~ x) +
  labs(title = "Aiden Horner's 'Indep' calculaton is identitical to my Independent calculation.")
```

### Kyle's Data vs Horner's Data

```{r}
ggplot(joined.df, aes(x = Data, y = joinedRetrieval.data)) +
       geom_point() +
       geom_smooth(method = 'lm', formula = y ~ x) +
  labs(title = "Aiden Horner's 'Indep' calculaton is identitical to my Independent calculation.")
```

