---
title: "Survey"
date: "`r Sys.Date()`"
author: "Kyle Kurkela"
output: 
  html_document:
    toc: yes
    toc_float: yes
    code_folding: hide
    df_print: paged    
---

```{r setup, echo=FALSE}
# requirements
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(corrplot))

# data
tidy.bias     <- read_rds(file = 'tidy_data/tidy_bias.rds')
tidy.sam      <- read_rds(file = 'tidy_data/tidy_sam.rds')
tidy.iri      <- read_rds(file = 'tidy_data/tidy_iri.rds')
tidy.vivq     <- read_rds(file = 'tidy_data/tidy_vviq.rds')

```

```{r tidy_chunk, echo=FALSE}
# minor tidying

tidy.vivq %>%
  rename(visual_imagery = response) -> tidy.vivq

left_join(tidy.bias, tidy.sam, by = 'subject_id') %>%
  left_join(tidy.iri, by = 'subject_id') %>%
  left_join(tidy.vivq, by = 'subject_id') -> df
```

```{r echo = FALSE}
# analysis
df %>%
  ungroup() %>%
  dplyr::select(-subject_id) %>%
  corrr::correlate(quiet = T) -> corr_mat

df %>%
  ungroup() %>%
  dplyr::select(-subject_id) %>%
  corrplot::cor.mtest() %>%
  magrittr::extract2('p') %>%
  `diag<-`(1) %>%
  corrr::as_cordf() %>%
  corrr::shave(upper = F) %>%
  corrr::stretch(na.rm = T) %>%
  rename(p = r) -> p

corr_mat %>%
  corrr::shave(upper = F) %>%
  corrr::stretch(na.rm = T) %>%
  left_join(p, by = c('x','y')) -> corr_df
```

## Raw Correlation Matrix

```{r, echo=FALSE,warning=FALSE,message=FALSE}
corr_df %>%
  ggplot(aes(x = x, y = y, fill = r)) +
  geom_raster() +
  geom_text(aes(label = round(r, 2)), color = 'black') +
  scale_fill_gradient2() +
  scale_x_discrete(limits = rev(corr_mat$term)) +
  scale_y_discrete(limits = rev(corr_mat$term)) +
  guides(fill = 'none') +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), axis.title = element_blank())
```

## Correlation Matrix Highlighting p < 0.05

```{r, echo=FALSE,warning=FALSE,message=FALSE}
corr_df %>%
  ggplot(aes(x = x, y = y, fill = r, alpha = p < 0.05)) +
  geom_raster() +
  geom_text(aes(label = round(r, 2)), color = 'black') +
  scale_fill_gradient2() +
  scale_x_discrete(limits = rev(corr_mat$term)) +
  scale_y_discrete(limits = rev(corr_mat$term)) +
  theme_classic() +
  guides(fill = 'none', alpha = 'none') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), axis.title = element_blank())
```

where:

| variable | description | 
| ----     | ----------  |
`famous person` | average dependency on famous person triads. |
`famous place` | average dependency on famous place triads. |
`bias` | `famous place` - `famous person`. |
`episodic` | sum total score on SAM-episodic subscale. |
`future` | sum total score on SAM-episodic subscale. |
`semantic` | sum total score on SAM-episodic subscale. |
`spatial` | sum total score on SAM-episodic subscale. |
`EC` | sum total score on IRI: Empathetic Concern subscale. "the tendency to experience feelings of sympathy and compassion for unfortunate others" |
`FS` | sum total score on IRI: Fantasy subscale. "the tendency to imaginatively transpose oneself into fictional situations" |
`PD` | sum total score on IRI: Personal Distress subscale. "the tendency to experience distress and discomfort in response to extreme distress in others" |
`PT` | sum total score on IRI: Perspective Taking subscale. "the tendency to spontaneously adopt the psychological point of view of others in everyday life" |
`visual_imagery` | sum total score on the VVIQ. |